A New Metropolis-Hastings Test for Fast Minibatch MCMC Inference and Optimization

### 2016-05-16 nips_2016.tex
start experiment

In this section, we use three experiments to reveal the benefits of our mini-batch MH testing. For the first experiment, we illustrate that our mini-batch MH testing can 
\subsection{Mixture of Gaussians}\label{ssec:gaussians}

>>>>

In this section, we use three experiments to reveal the benefits of our mini-batch MH testing. For the first experiment, we illustrate that our mini-batch MH testing can obtain the posterior distribution which is very close to the ideal one. For the second experiment, we use Logistic regression to reveal that our mini-batch sampler is much more efficient than adaptive minibatch approach. The third experiment shows that with the help of temperature, our mini-batch MH testing can be used to obtain the parameters which are close to MAP. 
\subsection{Mixture of Gaussians}\label{ssec:gaussians}
